Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2014-12-18 content/background.tex
uncommenting rest of comments

\commentout{
\begin{example}
  Consider the program in Listing~\ref{list:examplejava}. The supergraph corresponding to that program is shown in Figure~\ref{fig:examplesupergraph}.
  \otodo{Can we merge the examples from Figures 1 and 2 into a single example program?}
\otodo{I think we can remove the supergraph Figure 3.}
\begin{figure}
  \centering
  \begin{minipage}{\textwidth}
    \inputMinted{java}{examplesupergraph.java}
  \end{minipage}
  \caption{An example Java program}
  \label{list:examplejava}
\end{figure}

@@

\mtodo{The figure that we deleted was constructed so that there would be a realizable and a non-realizable path. Now that we deleted that figure, let's delete this example as well.}

@@

\commentout{
A practical implementation of the IFDS algorithm generally takes as input a representation of the
exploded supergraph edges $E^\sharp$ instead of explicit dataflow functions $M_F$. This is convenient because
the two are equivalent in expressiveness, and because the IFDS algorithm works internally with the exploded
supergraph. More specifically, the input generally provides a function
$f: N^* \times D \times N^* \to 2^D$. Given a (non-exploded) supergraph edge $n \to n'$ and a dataflow fact $d$,
$f(n,d,n')$ returns the set of all $d'$ such that the exploded supergraph contains the edge $(n,d) \to (n',d')$.
For convenience, the function $f$ can be split up into separate functions that handle the cases when
the $n\to n'$ is an intraprocedural edge, a call-to-start edge, or an end-to-return edge.\mtodo{Do we leave the start-to-return edge out as a special case of intraprocedural edge?}
}

@@

\mtodo{I think the rest of this section will not make sense to anyone who does not already understand it. Should I try to replace it with one paragraph that tries to give an intuitive understanding of what the IDE algorithm is doing?}
The overall idea behind computing the lattice elements $l_{n,\,d}$ is the following. For each interprocedurally realizable path
\[
  p=\left[(\startmain,\,\mathbf0),\,(n_1,\,d_1),\,\dots,\,(n_k,\,d_k)\right]
\]
 that starts with the entrypoint of the exploded supergraph, we compute the micro function $f_p$ that corresponds to $p$. The micro function consists of the composition of all individual micro functions with which the edges of $p$ are labeled:
\begin{align}
  f_p=\textsf{EdgeFn}((n_{k-1},\,d_{k-1}),\,(n_k,\,d_k))\,\circ\ldots\circ
      \textsf{EdgeFn}(\startmain,\,\mathbf0),\,(n_1,\,d_1))\,.
\end{align}

@@

\commentout{
\ftodo{Would it make sense to discuss an example of an IDE problem here?  Perhaps we can do this
  without using much space by referring to an existing figure elsewhere in the paper?}
  \otodo{See Example 4 on the previous page.}
  \otodo{Now done in Example 5.}
}

>>>>

\commentout{
\begin{example}
  Consider the program in Listing~\ref{list:examplejava}. The supergraph corresponding to that program is shown in Figure~\ref{fig:examplesupergraph}.
  %\otodo{Can we merge the examples from Figures 1 and 2 into a single example program?}
%\otodo{I think we can remove the supergraph Figure 3.}
\begin{figure}
  \centering
  \begin{minipage}{\textwidth}
    \inputMinted{java}{examplesupergraph.java}
  \end{minipage}
  \caption{An example Java program}
  \label{list:examplejava}
\end{figure}

@@

@@

\commentout{
A practical implementation of the IFDS algorithm generally takes as input a representation of the
exploded supergraph edges $E^\sharp$ instead of explicit dataflow functions $M_F$. This is convenient because
the two are equivalent in expressiveness, and because the IFDS algorithm works internally with the exploded
supergraph. More specifically, the input generally provides a function
$f: N^* \times D \times N^* \to 2^D$. Given a (non-exploded) supergraph edge $n \to n'$ and a dataflow fact $d$,
$f(n,d,n')$ returns the set of all $d'$ such that the exploded supergraph contains the edge $(n,d) \to (n',d')$.
For convenience, the function $f$ can be split up into separate functions that handle the cases when
the $n\to n'$ is an intraprocedural edge, a call-to-start edge, or an end-to-return edge.
%\mtodo{Do we leave the start-to-return edge out as a special case of intraprocedural edge?}
}

@@

The overall idea behind computing the lattice elements $l_{n,\,d}$ is the following. For each interprocedurally realizable path
\[
  p=\left[(\startmain,\,\mathbf0),\,(n_1,\,d_1),\,\dots,\,(n_k,\,d_k)\right]
\]
 that starts with the entrypoint of the exploded supergraph, we compute the micro function $f_p$ that corresponds to $p$. The micro function consists of the composition of all individual micro functions with which the edges of $p$ are labeled:
\begin{align}
  f_p=\textsf{EdgeFn}((n_{k-1},\,d_{k-1}),\,(n_k,\,d_k))\,\circ\ldots\circ
      \textsf{EdgeFn}(\startmain,\,\mathbf0),\,(n_1,\,d_1))\,.
\end{align}

@@

%\ftodo{Would it make sense to discuss an example of an IDE problem here?  Perhaps we can do this
%  without using much space by referring to an existing figure elsewhere in the paper?}
%  \otodo{See Example 4 on the previous page.}
%  \otodo{Now done in Example 5.}
